\documentclass[11pt,a4paper]{moderncv}
\usepackage[scale=0.8]{geometry}

\usepackage[T2A]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage[english]{babel}


\usepackage{graphicx}

\usepackage{cite}

\usepackage{epstopdf}

\renewcommand{\rmdefault}{cmr}
\renewcommand{\sfdefault}{cmss}
\renewcommand{\ttdefault}{cmtt}

\makeatletter
\newcommand{\rmnum}[1]{\romannumeral #1}
\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother

\moderncvtheme[green]{casual}



\firstname{Ilya}
\familyname{Menshikov}
\mobile{+7~(922)~146~65~28}
\email{unkmas@gmail.com}
\quote{Gentle I.}

\makeatletter

\begin{document}
\maketitle

\section{About}
\cvitem{Intro} {
  Hey there! My name is Ilya Menshikov, I'm web-developer.
}
\cvitem{} {
  For the last 6 years I have been working as web developer on Ruby. The largest project I worked at was PULSCEN.RU.
}
\cvitem{} {
  Recently, I have been also doing research in the field of computational linguistics. The topics of my research were sentiment analysis and approaches to automated thesauri construction.
}

\cvitem{Goals} {
  To grow up to top developer
}

\cvitem{Hobby}{
  I love music, programming, science and coffee. I'm playing in the board games and doing magic.
}

\section{Education}

\cventry{2015---}
  {PhD, 09.06.01}
  {Institute of Fundamental Education, Ural Federal University}
  {Yekaterinburg, Russia}
{}{}
\cventry{2013---2015}
  {Master of Information Systems}
  {Institute of Fundamental Education, Ural Federal University}
  {Yekaterinburg, Russia}
{}{}
\cventry{2009---2013}
  {Bachelor of Information Systems}
  {Institute of Physics and Technology, Ural Federal University}
  {Yekaterinburg, Russia}
{}{}

\section{Work Experience}

\cventry{2016---}
  {Developer}{}
  {SKB-Kontur}
  {}
{
\begin{itemize}
  \item Backend developmet on Ruby language;
  \item Frontend development;
  \item Development of a document management system for Decathlon company
  \item Development of bank guarantees issuance portal;
\end{itemize}
}

\cventry{2014---2016}
  {Developer}{}
  {Under NDA}
  {}
{
\begin{itemize}
  \item Backend development on Ruby language;
  \item Infrastructure automation and maintenance;
  \item Frontend development;
  \item Partially - project managment;
\end{itemize}
}

\cventry{2011---2014}
  {Developer}{Software Development Department}
  {ABAK--PRESS Publising House}
  {Yekaterinburg, Russia}
{
\begin{itemize}
  \item Development of the \href{http://pulscen.ru}{PULSCEN.ru} website using Ruby on Rails;
  \item Development of the \href{http://dkvartal.ru}{DKVARTAL.ru} website using Ruby on Rails;
  \item Initiation of the Functional and Unit Testing of the {DKVARTAL.ru};
  \item Creating a wiki-system and nlp algorythms at the {DKVARTAL.ru}.
  \item Creating some libraries on ruby language (Sitemap, EasyMailChimp)
\end{itemize}
}

\cvitem {}{}

\cventry{2011---2011}
  {Developer}{}
  {Elitmaster}
  {Yekaterinburg, Russia}
{
\begin{itemize}
  \item Development of the Yii-based CMS;
  \item Development of the corporate system for \href{1litr.elitmaster.com}{1litr};
  \item Development and support of a big variety of PHP web-sytes.
\end{itemize}
}


\section{Languages}
\cvlanguage{Russian}{Native}{}
\cvlanguage{English}{Intermediate}{}

\section{Skills}

\subsection{Programming languages}
\cvcomputer{Ruby}{Ruby~on~Rails, Sinatra}
{JavaScript}{JQuery}
\cvcomputer
{Had some expirience} {Go, Java, Python, C\#}
{}{}

\subsection{DB}
\cvcomputer{RDBMS}{PostgreSQL}
           {NoSQL}{Redis}

\subsection{Other}
\cvcomputer{Search Systems} {Elasticsearch}
           {SCM}{Git}

\section{Social and Professional Networks}
\cvitem{GitHub}{\href{https://github.com/unkmas}{github.com/unkmas}}{}{}
\cvitem{VK}{\href{http://vk.com/unkmas}{vk.com/unkmas}}{}{}

\section{Selected Awards and Achievements}

\cvitem{2013}{
  Winner of "The participant of the youth scientific innovation contest" grant contest.
}

\cvitem{2012}{
  Winner of "SKB Kontur grant competition".
}

\cvitem{2010}{
  Participant of the ACM International Collegiate Programming Contest.
}
\cvitem{2009}{
  Prizewinner of the USTU-UPI Research Exhibition.
}
\cvitem{2009}{
  Silver Certificate of the USTU--UPI Rector.
}
\cvitem{2009}{
  Gold Certificate of the USTU--UPI Rector.
}

\end{document}
